Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-25 snapshot_system/fast14_architecture.tex
update

PDS data is re-calculated periodically, but 
the total data size is small.  When
a new PDS data  set is computed, in-memory PDS index is replaced, but 
the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
The old data is not removed because they can still be referenced by the existing snapshots. 
A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months). 
\end{itemize}

>>>>

PDS data is re-calculated periodically, but 
the total data size is small.  When
a new PDS data  set is computed, in-memory PDS index is replaced, but 
the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
The old data is not removed because they can still be referenced by the existing snapshots. 
A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).

We decide not to take the sampled index appraoch~\cite{Guo2011} 
for detecting duplicates from PDS.
This is because for the data sets we have tested, we only observed very limited spatial locality 
among popular data chunks. On average the number of consecutive PDS index hits is lower than 7,
which is not sufficient to enable effective prefetching which is required for index sampling.
\end{itemize}

### 2013-09-25 snapshot_system/fast14_background.tex
revisions. moved from inner/cross-VM to local/global dedup
update

Since it is expensive to compare a large number of chunk signatures for deduplication,
several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}
and a parallel batch solution for cluster-based deduplication is 
studied in ~\cite{WeiZhangHotStorage13}. 
All of the above approaches have focused on optimization of deduplication
efficiency, and none of them have considered the impact
of deduplication on fault tolerance in the cluster-based environment that we have considered
in this paper.

@@

In designing a VC duplication algorithm, we have considered and adopted some of
the following previously-developed techniques.
1)
{\em Version-based change detection}.
VM snapshots can be  backed up  incrementally by identifying file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Such a scheme  is  VM-centric since deduplication is localized. 
We are seeking for a tradeoff since 
cross-VM  signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
2) {\em Stateless  data Routing}.
One approach for scalable duplicate comparison is to use a content-based hash
partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
that divides the deduplication work with a similarity approximation. This work 
is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
each request is routed  to a machine which holds
a Bloom filter  or can fetch on-disk index for additional comparison.
While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
VM-specific local search.
3) {\em Sampled Index}.
One effective approach that reduces memory usage is 
to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
To use a distributed memory version of the sampled index, every deduplication request
may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.

>>>>

Since it is expensive to compare a large number of chunk signatures for deduplication,
several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
and a parallel batch solution for cluster-based deduplication is 
studied in ~\cite{wei2013}. 
All of the above approaches have focused on optimization of deduplication
efficiency, and none of them have considered the impact
of deduplication on fault tolerance in the cluster-based environment that we have considered
in this paper.

@@

In designing a VC duplication algorithm, we have considered and adopted some of
the following previously-developed techniques.
1)
{\em Version-based change detection}.
VM snapshots can be  backed up  incrementally by identifying file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Such a scheme  is  VM-centric since deduplication is localized. 
We are seeking for a tradeoff since 
global signature comparison can deliver additional compression~\cite{Guo2011,Dong2011,extreme_binning09}.
2) {\em Stateless  data Routing}.
One approach for scalable duplicate comparison is to use a content-based hash
partitioning algorithm called stateless data routing by Dong et al.~\cite{Dong2011} 
that divides the deduplication work with a similarity approximation. This work 
is similar to Extreme Binning by Bhagwat et al.~\cite{extreme_binning09} and 
each request is routed  to a machine which holds
a Bloom filter  or can fetch on-disk index for additional comparison.
While this approach is VM-oblivious, it motivates us to  use  a combined signature of a dataset to narrow
VM-specific local search.
3) {\em Sampled Index}.
One effective approach that reduces memory usage is 
to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
The algorithm is VM oblivious and it is not easy  to adopt for a distributed architecture. 
To use a distributed memory version of the sampled index, every deduplication request
may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.

### 2013-09-25 snapshot_system/fast14_deduplication.tex
update

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{Jin2009},
we conduct additional local similary guided deduplication on a snapshot by comparing
chunk fingerprints of a dirty segment 
with those in  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their content signature is the same.
This segment content signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
content similarity is  an approximation~\cite{AdnriBroader}.  When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
which contain chunk fingerpints to be compared.
To control the time cost of search, we set a limit on the the number of  similar segments recipes to be fetched. 
% Then,
%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
%with those in similar segments.  
For a 2MB segment, its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
by limiting at most 10 similar segments to search, the amount of memory for maintaining those similar segment recipes is small.
As part of our local duplicate search we also compare the current segment
against the parent segment at the same offset.

@@

\begin{figure}
\centering
%\epsfig{file=log-log.disk,width=3in}
%source ../vm_snapshot_sim/images/log-log.disk.eps
 \includegraphics[width=3in]{figures/log-log-disk}
\caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
\label{fig:Datazipf}
\end{figure}
We decide not to take the sampled index appraoch~\cite{Guo2011} 
for detecting duplicates from PDS.
This is because for the data sets we have tested, we only observed very limited spatial locality 
among popular data chunks. On average the number of consecutive PDS index hits is lower than 7,
which is not sufficient to enable effective prefetching which is required for index sampling.

\begin{table}[htbp]
\centering
\begin{tabular}{|p{1.25cm}|p{5.5cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belong to  PDS\\
\hline
$p$ & the number of machines in the cluster\\
\hline
$V$ & the average number of VMs hosted on each machine\\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$C$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$ & the average number  of non-PDS file system blocks  in a VM for VC\\
\hline
$N_2$ & the average number  of PDS file system blocks  in a VM for VC\\
\hline
$N_o$ & the average number  of file system blocks  in a VM for VO\\
\hline
A(r) & the availability of a file system block with replication degree $r$\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

@@

%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
%let $c$ be the total number of data chunks. 
%$c_u$ be the total number of fingerprints 
%in the global index after complete deduplication, and
%$f_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $f_i = \frac{f_1}{i^\alpha}.$
Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
\[
f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
\]
Given $\alpha <1$, $f_1$ can be approximated with integration:
\begin{equation}
f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
\end{equation}

The  $k$ most popular fingerprints can cover the following number of chunks after local 
deduplication:
\[
f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
=c(1-\delta) \sigma^{1-\alpha}.
\]

Deduplication efficiency of the VC approach using top $k$ popular chunks
is the percentage of duplicates that can be detected:  
\begin{equation}
\label{eq:dedupeff}
%\begin{split}
%e_k &= 
\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
{c  - c_u }.\\
%\end{split}
\end{equation}

We store the popular index using a distributed shared memory hashtable such as Memcached
and allocate a fixed percentage of memory space   per physical machine for top $k$ popular items.
As the number of physical machines ($p$) increases,
the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
a constant because each physical machine on average still hosts a fixed constant number of 
VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
remains constant.
Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            width=\linewidth,
            height=0.6\linewidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.30)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{Predicted vs. actual PDS coverage as data size increases.}
  \label{fig:cds-coverage}
\end{figure}
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global deduplication due to PDS.
We call this PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
While the predicted value remains flat, the  real coverage actually increases as the data size
increases, which indicates that $\alpha$ increases with the data size. 
Thus in practice, the coverage of the PDS increases as more VMs are involved.

@@

The replication degree of the backup storage 
is $r$ for regular file blocks and $r=3$ is a typical setting in distributed
file systems~\cite{googlefs03,hdfs10}.
In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
$ k*r_c  + (c_u-k)*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
\[
\sigma \frac{r_c}{r} + 1-\sigma.
\]
Since $\sigma$ is small (it is 2\% in our experiments),  
term $\sigma \frac{r_c}{r}$ is small in the above expression.  
Thus the impact on storage increase is very small even when we choose a large $\frac{r_c}{r}$ ratio. 
For example, $\frac{r_c}{r}=2$ or 3.

Next we  assess  the impact of losing $d$ machines 
to the the VC and VO approaches.  
A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use file system blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probablity of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by the VM.

For VC, each VM has an average number of $N_1$ non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS file system block is associated with one VM
 and  we denote that PDS file system blocks are
shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Then, 
\[
V *p*N_1 *s  \approx c_u (1-\sigma)\; \mbox{ and } \; 
V *p*N_2 *s  \approx c_u \sigma V_c.
\]

@@

Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  From the above equations:
\[
\frac{N_1}{N_o} \approx  \frac{1-\sigma}{V_o}.
\]

Thus $N_1$ is much smaller than $N_o$. 
When there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
From data, we have observed that $N_1 +N_2 < N_o$ in practice. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
VMs sharing each file block on average in VO.

>>>>

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{Jin2009},
we conduct additional local similary guided deduplication on a snapshot by comparing
chunk fingerprints of a dirty segment 
with those in  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their content signature is the same.
This segment content signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot metadata (called recipe). Note that this definition of
content similarity is an approximation~\cite{resemblance97}.  When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
which contain chunk fingerpints to be compared.
To control the time cost of search, we set a limit on the the number of  similar segments recipes to be fetched. 
% Then,
%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
%with those in similar segments.  
For a 2MB segment, its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata,
by limiting at most 10 similar segments to search, the amount of memory for maintaining those similar segment recipes is small.
As part of our local duplicate search we also compare the current segment
against the parent segment at the same offset.

@@

\begin{figure}
\centering
%\epsfig{file=log-log.disk,width=3in}
%source ../vm_snapshot_sim/images/log-log.disk.eps
 \includegraphics[width=3in]{figures/log-log-disk}
\caption{Duplicate frequency versus  chunk ranking in a log scale after local deduplication.}
\label{fig:Datazipf}
\end{figure}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|p{1.25cm}|p{5.5cm}|}
\hline
$k$ &  the number of top most popular chunks selected for deduplication\\ 
\hline
$c$ &  the total amount of data chunks in a cluster of VMs\\ 
\hline
$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
\hline
$f_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in local deduplication\\
\hline
$\sigma$ & =$\frac{k}{c_u}$ which is  the percentage of unique data  belong to  PDS\\
\hline
$p$ & the number of machines in the cluster\\
% \hline
% $V$ & the average number of VMs hosted on each machine\\
\hline
$E$ & the deduplication efficiency of VC approach\\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$C$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average size of file system blocks in the distributed file system. The default is  64MB.\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$ & the average number  of non-PDS file system blocks  in a VM for VC\\
\hline
$N_2$ & the average number  of PDS file system blocks  in a VM for VC\\
\hline
$N_o$ & the average number  of file system blocks  in a VM for VO\\
\hline
A(r) & the availability of a file system block with replication degree $r$\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

%Table~\ref{tab:symbol} defines paramters $c$, $c_u$, $f_i$, and $\delta$ used below.
%let $c$ be the total number of data chunks. 
%$c_u$ be the total number of fingerprints 
%in the global index after complete deduplication, and
%$f_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $f_i = {f_1}/{i^\alpha}.$
The total amount of chunks reside in our backup storage which
has local duplicates excluded is $c (1-\delta)$, this can be represented
as the sum of each unique fingerprint times its frequency:
%Since $ \sum_{i=1}^{c_u}f_i = c (1-\delta)$,
\[
f_1 \sum_{i=1}^{c_u}\frac{1}{i^\alpha} = c (1-\delta).
\]
Given $\alpha <1$, $f_1$ can be approximated with integration:
\begin{equation}
f_1=\frac{c(1-\alpha)(1-\delta)}{c_u^{1-\alpha}}.
\end{equation}

Thus putting the $k$ most popular fingerprints into PDS index can remove the following number of chunks during global 
deduplication:
\[
f_1 \sum_{i=1}^{k}\frac{1}{i^\alpha} \approx  
f_1 \int_{1}^{k}\frac{1}{x^\alpha} dx  \approx  f_1\frac{  k^{1-\alpha}} {1-\alpha}
=c(1-\delta) \sigma^{1-\alpha}.
\]

Deduplication efficiency of the VC approach using top $k$ popular chunks
is the percentage of duplicates that can be detected:  
\begin{equation}
\label{eq:dedupeff}
%\begin{split}
%e_k &= 
E=\frac{ c\delta + c(1-\delta) \sigma^{1-\alpha}}
{c  - c_u }.\\
%\end{split}
\end{equation}

% After the global deduplication, the number of remaining chunks is:
% \[
% c-E(c-c_u)
% \]

We store the PDS index using a distributed shared memory hashtable such as Memcached
and allocate a fixed percentage of memory space per physical machine for top $k$ popular items.
As the number of physical machines ($p$) increases,
the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
a constant because each physical machine on average still hosts a fixed constant number of 
VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
remains constant.
Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={PDS Coverage},
            width=\linewidth,
            height=0.6\linewidth,
            cycle multi list={
                mline\nextlist
                [3 of]mmark*\nextlist
            },
            %cycle list name=mcolor,
            xlabel={Total num. chunks stored (in billions)},
            ylabel={PDS Coverage (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            %legend pos=outer north east,
            legend columns=2,
            legend style={
                at={(0.5,-0.30)},
            anchor=north},
            ]
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=A4] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T1] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T2] {figures/cds_coverage.txt};
            \addplot table[x expr=\thisrow{InputChunks}/1000000000,y=T4] {figures/cds_coverage.txt};
            \legend{Measured ($\sigma=1\%$),Measured ($\sigma=2\%$),Measured ($\sigma=4\%$),Predicted ($\sigma=1\%$),Predicted ($\sigma=2\%$),Predicted ($\sigma=4\%$)};
            \end{axis}
    \end{tikzpicture}
  \caption{Predicted vs. actual PDS coverage as data size increases.}
  \label{fig:cds-coverage}
\end{figure}
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global deduplication due to PDS.
We call this PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed at
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents memory usage of approximately 100MB memory per machine for the PDS.
While the predicted value remains flat, the  real coverage actually increases as the data size
increases, which indicates that $\alpha$ increases with the data size. 
Therefore in practice, the coverage of the PDS increases as more VMs are involved.

@@

The replication degree of the backup storage 
is $r$ for regular file blocks and $r=3$ is a typical setting in distributed
file systems~\cite{googlefs03,hdfs10}.
In the VC approach, a special replication degree $r_c$ is used for PDS data where $r_c>r$. 
The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
$ k*r_c  + (c-E(c-c_u))*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
\[
\sigma \frac{r_c}{r} + \frac{c-e(c-c_u)}{c_u}.
\]
Since $\sigma$ is small (it is 2\% in our experiments),  
term $\sigma \frac{r_c}{r}$ is small in the above expression.  
Thus the impact on storage increase is very small even when we choose a large $r_c/r$ ratio. 
For example, $r_c/r=2$ or 3.

Next we  assess  the impact of losing $d$ machines 
to the the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use file system blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probablity of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by the VM.

For VC, each VM has an average number of $N_1$ non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS file system block is associated with one VM
 and  we denote that PDS file system blocks are
shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block, 
$V$ be the average number of VMs hosted on each machine. Then, 
\[
V *p*N_1 *s  \approx c-E(c-c_u)\; \mbox{ and } \; 
V *p*N_2 *s  \approx c_u \sigma V_c.
\]

@@

Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  From the above equations:
\[
\frac{N_1}{N_o} \approx  \frac{c-E(c-c_u)}{c_uV_o}.
\]

If we achieve very high deduplication efficiecny, then $N_1$ would be much smaller than $N_o$. 
When there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
From data, we have observed that $N_1 +N_2 < N_o$ in practice. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
Note that  if  the backup for multiple VMs were conducted concurrently, there could be many more
VMs sharing each file block on average in VO.
